Deep Learning and Bayesian Modeling

### 2021-05-24 DeepLearningAndBayesianSoftware.Rmd
added in Oriol thanks, added the group queries, typo fixes

Reading from top of Fig 1, assuming raw research citations counts matter, Bayesian packages are overwhelmed by deep learning packages with a count of nearly 35,000 citations to a Bayesian count of 4,500--nearly a 10x difference. One could excuse a bit of Bayesian despondency in the face of the wave depicted above--this ratio supports my expectations. But graph also shows relative counts for research citations outside of computer science which drops the count of deep learning from 34,977 to 8,885--a 75% drop. That drop IS a surprise.  I didn't have a prior on deep learning's distribution across subject categories but I didn't expect it to be so skewed. The Bayesian ecosystem shows a total of 4,578 of which 14% are computer science--that drop does not surprise me.

@@

Staring with the subject that got us here we see that computer science has 728 Bayesian publications vs 29,301 deep learning publications for 98% of the share of 30,029 total. The left most two columns are the same queries used for the graph in Fig 1 with the total in column 3. Columns 4-12 are individual packages with percentage of the total in the 13th column.  Sticking with computer science, one sees that TensorFlow has 18,178 references with 51% of the count--note that the total counts are higher because an article can matched by more that one query, each package gets a query, so the article count is 3 if Keras, PyMC and TensorFlow queries match the references and it has a computer science subject classification.

@@

```{r Query Table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
pkg_query_m_display <- pkg_query_m
pkg_query_m_display[,2] <- sprintf("REF(%s)", str_replace_all(pkg_query_m[,2], '\\+',' '))

@@

@@

I'd like to thank the Andrew Gelman's Laplace lab at Columbia University for support.

>>>>

Reading from top of Fig 1, assuming raw research citations counts matter, Bayesian packages are overwhelmed by deep learning packages with a count of nearly 35,000 citations to a Bayesian count of 4,600--nearly a 10x difference. One could excuse a bit of Bayesian despondency in the face of the wave depicted above--this ratio supports my expectations. But graph also shows relative counts for research citations outside of computer science which drops the count of deep learning from 35k to 8.8k--a 75% drop. That drop IS a surprise.  I didn't have a prior on deep learning's distribution across subject categories but I didn't expect it to be so skewed. The Bayesian ecosystem shows a total of 4.5k of which 14% are computer science--that ratio does not surprise me.

@@

Staring with the subject that got us here we see that computer science has 727 Bayesian publications vs 29,365 deep learning publications for 98% of the share of 30,092 total. The left most two columns are the same queries used for the graph in Fig 1 with the total in column 3. Columns 4-12 are individual packages with percentage of the total in the 13th column.  Sticking with computer science, one sees that TensorFlow has 18,178 references with 51% of the count--note that the total counts are higher because an article can matched by more that one query, each package gets a query, so the article count is 3 if Keras, PyMC and TensorFlow queries match the references and it has a computer science subject classification.

@@

```{r Query Table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
pkg_query_m_display <- rbind(pkg_query_m, queryBayVsDeepM)
pkg_query_m_display[,2] <- sprintf("REF(%s)", str_replace_all(pkg_query_m_display[,2], '\\+',' '))

@@

The above queries can be run with the advance search option at https://scopus.com and are generated from the API queries actually used. The change is replacing '+' with ' '. An account is required which is included for many education institutions.

@@

I'd like to thank Andrew Gelman and the Laplace lab at Columbia University for support.

Oriol Abril Pla brought up emcee as a popular Bayesian system worth consideration which was a big oversight on my part as well as providing insightful commentary.
